%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass{cv} % Use the custom resume.cls style
% \documentclass[letterpaper, 8pt]{article}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{english}
\usepackage{kotex} %kotex package를 사용해야 한국어를 입력할수 있습니다!
% 한글 전체를 기본 고딕으로
\renewcommand{\rmdefault}{cmss} % 기본 글꼴을 sans-serif 계열로
\renewcommand{\sfdefault}{cmss}

% Korean font setup - replace 'NanumMyeongjo' with any Korean font installed on your system
% \newfontfamily\koreanfont{NanumMyeongjo}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[normalem]{ulem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{etaremune}  % 역순 리스트용 패키지
\input{glyphtounicode}

\usepackage{natbib}
\usepackage{bibentry}
\nobibliography*
% the below is to make domestic bib items to have bullet instead of [1]
\makeatletter
\renewcommand\@biblabel[1]{\textbullet}
\makeatother

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% cmd.tex (Custom commands inlined)
%-------------------------

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingFourLines}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
      \textit{\small #5} & \textit{\small #6} \\
      \textit{\small #7} & \textit{\small #8} \\
    \end{tabular*}
  \vspace{-4pt}
}

\newcommand{\resumeSubheadingFiveLines}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
  \vspace{-4pt}
}

\newcommand{\resumeSubheadingThreeLines}[6]{
    \vspace{-2pt}
    \item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
        \textit{\small#5} & \textit{\small #6}
    \end{tabular*}
    \vspace{-4pt}
}

\newcommand{\resumeSubheadingTwoLines}[4]{
 \vspace{-2pt}\item
 \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #2 \\
  \textit{\small#3} & \textit{\small #4}
  \end{tabular*}
  \vspace{-4pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}
    \vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
\begin{document}

%-------------------------
% heading
%-------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://sites.google.com/view/aprl-dgist/home}{ }} & Email : \href{mailto:gsk@dgist.ac.kr}{gsk@dgist.ac.kr} \\
  {} & \href{https://sites.google.com/view/aprl-dgist/home}{\underline{Lab Website}} \\
  {} & \href{https://scholar.google.com/citations?user=9mKOLX8AAAAJ&hl=en}{\underline{Google Scholar}} \\
\end{tabular*}

\vspace{-7mm}
\begin{center}
    \textbf{\Huge \scshape Giseop KIM}
\end{center}
\vspace{-1mm}

%-------------------------
% positions
%-------------------------
\section{Positions}
  \resumeSubHeadingListStart
    \item
    \vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\href{https://sites.google.com/view/aprl-dgist/home}{PI of Autonomy and Perceptual Robotics Lab (APRL), DGIST}} & Dec. 2024 -- Present \\
      \textit{\small Assistant Professor, Dept. of Robotics and Mechatronics Eng., DGIST} & \textit{\small Daegu, South Korea} \\
      \textit{\small \ \ Joint Appointment, Physical AI Center, DGIST} & \\
      \textit{\small \ \ Joint Appointment, Department of Artificial Intelligence, DGIST} & \\
      \textit{\small \ \ Joint Appointment, Mechanical Engineering Track, Undergraduate School, DGIST} & \\
    \end{tabular*}
    \vspace{-4pt}

    \vspace{1mm}
    \resumeSubheadingTwoLines
      {Research Scientist, NAVER LABS}{Dec. 2021 -- Dec. 2024}
      {Autonomous Driving Group (2021 -- 2023) and Vision Group (2024), NAVER LABS}{Seongnam, South Korea}

    \vspace{1mm}
    \resumeSubheadingTwoLines
      {Graduate Student Researcher, KAIST}{Mar. 2017 -- Aug. 2021}
      {\href{https://rpm.snu.ac.kr}{Intelligent Robotic Autonomy and Perception (IRAP) Lab}, Dept. of Civil and Environmental Eng., KAIST}{Daejeon, South Korea}

    \resumeSubHeadingListEnd

%-------------------------
% research_interests
%-------------------------
\section{Research Interests}

\ Simultaneous localization and mapping (SLAM), 3D reconstruction, Digital twin, Mobile robot navigation, Social robot navigation, Visual-language navigation, Neural map representation, Sensor-fusion, Inertial-aided navigation, Autonomous vehicles, 3D perception, Spatial AI, Physical AI, etc.

%-------------------------
% education
%-------------------------
\section{Education}

  \resumeSubHeadingListStart
    \resumeSubheadingFourLines
      {Korea Advanced Institute of Science and Technology (KAIST)}{Feb. 2022}
      {PhD in Civil and Environmental Engineering (CEE)}{ }
      {\ \ Dissertation: ``LiDAR-based Lifelong Robotic Mapping in Changing Environments"}{}
      {\ \ Advised by Dr. Youngchul Kim and Dr. \href{https://ayoungk.github.io}{Ayoung Kim}}{}
        % \vspace{1mm}
    \resumeSubheadingFourLines
      {Korea Advanced Institute of Science and Technology (KAIST)}{Feb. 2019}
      {MS in Civil and Environmental Engineering (CEE)}{ }
      {\ \ Dissertation: ``Isovist-induced Robust LiDAR Localization"}{}
      {\ \ Advised by Dr. Ayoung Kim}{}
    % \vspace{1mm}
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Feb. 2017}
      {BS in Civil and Environmental Engineering (CEE)}{ }
  \resumeSubHeadingListEnd

%-------------------------
% research_supervision
%-------------------------
\section{Research Supervision}

\begin{itemize}[label=$\cdot$]
  \item Postdoctoral Researcher (1): Nayak Bibhutibhusan (2025 Fall--)
  \vspace{-1mm}
  \item Integrated MS--PhD Students (1): Bokeon Suh (2025 Fall--)
  \vspace{-1mm}
  \item PhD Students (1): Doyeon Kim (2026 Spring--)
  \vspace{-1mm}
  \item MS Students (5): Jiseon Kim (2025 Fall--), Yumin Lee (2025 Fall--), Hyoseok Ju (2025 Fall--), Hoyoon Kim (2026 Spring--), Beomsoo Kim (2026 Spring--)
  \vspace{-1mm}
  \item Undergraduate Interns: Yewon Kim (2026 Spring), Ayun Lee (2026 Spring), Hyeonwoo Jeong (2026 Winter)
\end{itemize}

%-------------------------
% publications
%-------------------------
\section{Selected Publications}

% \begin{pubSubsectionNum}{Dissertations}
%   \item \bibentry{gkim-phdthesis}
%   \item \bibentry{gkim-msthesis}
% \end{pubSubsectionNum}

\begin{pubSubsectionNum}{Book Chapters}
  \item \href{http://asrl.utias.utoronto.ca/~tdb/slam/}{\bibentry{sh-ch8-lidar}}
\end{pubSubsectionNum}

\vspace{-2mm}
\begin{pubSubsectionNum}{International Journal}
  \item \bibentry{lee2025lamp}
  \item \bibentry{kim2024sr}
  \item \bibentry{kim2024solid}
  \item \bibentry{jung2023helipr}
  \item \bibentry{kim2021scan}
  \item \bibentry{cho2022openstreetmap}
  \item \bibentry{kim20191}
  \item \bibentry{gkim-2019-ceus}
\end{pubSubsectionNum}

\vspace{-2mm}
\begin{pubSubsectionNum}{International Conference Proceedings}
  \item \bibentry{ju2026scalemaster}
  \item \bibentry{mkim2026iclr}
  \item \bibentry{kim2025transparent}
  \item \bibentry{elite2025}
  \item \bibentry{kim2024broad}
  \item \bibentry{lim2023orora}
  \item \bibentry{yun2022sthereo}
  \item \bibentry{kim2022lt}
  \item \bibentry{kim2020remove}
  \item \bibentry{kim2020mulran}
  \item \bibentry{cho2020unsupervised}
  \item \bibentry{kim2018scan}
\end{pubSubsectionNum}

\vspace{-2mm}
\begin{pubSubsectionNum}{Domestic Journal}
  \item \bibentry{suh2026vlm}
\end{pubSubsectionNum}

%-------------------------
% funded_projects
%-------------------------
\section{Funded Projects}

\vspace{1mm}
\begin{pubSubsectionNum}{Ongoing}
    \item 2026--2030. Title: Young Researcher Program (Type B) -- Multi-Robot Autonomy with Implicit Human Interaction (AIMS). Funded by: National Research Foundation (NRF) of Korea. Role: PI.
    \vspace{-1mm}
    \item 2025 (6 months, Jul to Dec). Title: N-HRHR (High-risk High-return project), DGIST. Funded by: DGIST. Role: PI.
    \vspace{-1mm}
    \item 2025--2029. Title: InnoCORE Research Program (DGIST Team topic: Physical AI for Bio-Embodied Systems). Funded by: Ministry of Science and ICT, South Korea. Role: Core Researcher, DGIST.
    \vspace{-1mm}
    \item 2025--2030. Title: AI Star Fellowship Program (Top-tier Young AI Researcher Support). Funded by: Ministry of Science and ICT, South Korea. Role: Core Researcher, DGIST.
    \vspace{-1mm}
    \item 2025--2028. Title: Start-up Fund. Funded by: DGIST. Role: PI.
    \vspace{-1mm}
\end{pubSubsectionNum}

% \begin{pubSubsectionNum}{Completed}
%     \item TBA
% \end{pubSubsectionNum}

% \begin{pubSubsectionNum}{Before DGIST (--2021)}
%     \item 2021. Title: Development of technology for analyzing and predicting disaster risks in urban spaces of urban regeneration areas. Funded by: KAIA, MOLIT of South Korea (in total 1,796,000,000 KRW). Role: Developing portable 3D mapping system and software.
%     \vspace{-1mm}
%     \item 2020--2021. Title: Towards long-term autonomy through introduction of the temporal domain into spatial representations used in robotics. Funded by: Bilateral Research Exchange Support Program of NRF, South Korea (in total 40,000,000 KRW) and The Czech Science Foundation (GACR). Role: Joint research with Professor Tomas Krajnik of Czech Technical University in Prague.
%     \vspace{-1mm}
%     \item 2018--2020, Title: Localization techniques on 3D SLAM maps using LiDAR and Camera sensors (2018), Development of SLAM technology based on LiDAR and Camera sensors using deep learning (2019), Localization in changing city (2020). Funded by: NAVER LABS. Role: Lead researcher.
%     \vspace{-1mm}
%     \item 2018--2019. Title: Automated urban analysis techniques using 3D sensor data (creation of 100m scale perceptible regions and topological maps). Funded by: KAIA, MOLIT of South Korea (in total 370,000,000 KRW). Role: Lead researcher.
%     \vspace{-1mm}
%     \item 2018. Title: 3A Localization -- Anytime Anywhere Anyview Robot Localization at Complex Urban. Funded by Master's and Doctorate Adventure Research Project, KAIST (in total 4,500,000 KRW). Role: Lead researcher.
% \end{pubSubsectionNum}

%-------------------------
% teaching
%-------------------------
\section{Teaching}

\begin{pubSubsectionNum}{Lectures}
    \item RT604 Advanced Mobile System (Spring 2026)
    \item MECH301 Robots for Human (Spring 2026)
    \item MECH307 Introduction to Artificial Intelligence (Fall 2025)
    \item AT603 Introduction to Mobility Engineering (Fall 2025)
    \item BE203 Creative Mechanical Design (Spring 2025)
\end{pubSubsectionNum}

%-------------------------
% academic_services
%-------------------------
\section{Academic Services}

\begin{pubSubsection}{Reviewer}
    \item Journals: T-RO, RA-L, IJRR, IJCV, T-ASE, T-II, T-AES, etc.
    \vspace{-1mm}
    \item Conferences: ICRA, IROS, RSS, CVPR, ICCV, ECCV, UR, etc.
\end{pubSubsection}

\vspace{-2mm}
\begin{pubSubsectionNum}{Editorial Board}
    \item Associate Editor: International Conference on Ubiquitous Robots (UR) (2022--2024)
\end{pubSubsectionNum}

\vspace{-2mm}
\begin{pubSubsectionNum}{Organizing Committee}
    \item Tutorial Organizer: \href{}{Spatial AI Tutorial}, KRoC 2026 (Pyeongchang, South Korea)
    \vspace{-1mm}
    \item Program Committee: ICROS 2026 (Daegu, South Korea)
\end{pubSubsectionNum}

%-------------------------
% awards
%-------------------------
\section{Awards}

\begin{itemize}[label=$\cdot$]
    \item Early-career Researcher Award, KRoC 2026 (The 21st Korea Robotics Conference), 2026
    \vspace{-1mm}
    \item \href{}{Best Poster Award}, HEAI Workshop at IROS 2025
    \vspace{-1mm}
    \item Best paper award at ICRA 2018 workshop of Long-term autonomy and deployment of intelligent robots in the real-world
\end{itemize}

%-------------------------
% patents
%-------------------------
\section{Patents}

\vspace{1mm}
\begin{pubSubsectionNum}{}

    \item Title: Method and Apparatus for Automation of Urban Visibility Analysis Using 3D Sensor Data (Registered in South Korea, 2019, 10-1973903-0000)
    \vspace{-1mm}
    \item Title: Encoder Frame Device And Vehicle Odometry Measurement System Using The Same (Registered in South Korea, 2019, 10-1994339-0000)

\end{pubSubsectionNum}

%-------------------------
% leadership
%-------------------------
\section{Leadership}

\vspace{1mm}
\begin{pubSubsectionNum}{}
    \item Mentor for Research Interns at NAVER LABS (2023)
    \vspace{-1mm}
    \item Department Student President of Civil and Environmental Engineering Dept., KAIST (2015)
\end{pubSubsectionNum}

%-------------------------
% invited_talks
%-------------------------
\section{Invited Talks}
\begin{itemize}[label=$\cdot$]

    \item 2026.03.24: Invited Talk, ETRI Daegu-Gyeongbuk Regional Research Division
    \hfill (Title: \textit{Memory-Augmented Spatial Intelligence for Autonomous Robot Navigation})

    \item 2026.02.05--06: Spatial AI Tutorial Organizer \& Speaker, KRoC 2026, Pyeongchang
    \hfill (Title: \textit{IMU Basics and Inertial Aided Navigation})

    \item 2026.02.05: Early-career Researcher Award Session, KRoC 2026, Pyeongchang
    \hfill (Title: \textit{Memory-Augmented Spatial Intelligence for Autonomous Robot Navigation})

    \item 2026.02.05: Special Session 3: AI-based Autonomous Systems, KRoC 2026, Pyeongchang
    \hfill (Title: \textit{CoT/Scene-graph/and Recent Paradigms for Mobile Robot Navigation})

    \item 2026.02.02: Invited Talk, Dalseo-gu Office Monthly Meeting Special Lecture, Daegu
    \hfill (Title: \textit{\textsf{대구의 혁신, 로봇과 미래 모빌리티 도시로 향하다}})

    \item 2026.01.19: Invited Tutorial, ICEIC 2026, Macau, China
    \hfill (Title: \textit{An Invitation to 3D Vision, Spatial AI, and Physical AI})

    \item 2025.12.10: Invited Talk, Dept. of Intelligent Robotics, SKKU, Suwon
    \hfill (Title: \textit{SLAM, Spatial AI, and Human-Robot Interactive Navigation})

    \item 2025.12.09: Invited Talk, Dept. of Civil and Environmental Eng., KAIST, Daejeon
    \hfill (Title: \textit{Robotics and Spatial AI for Construction})

    \item 2025.12.08: Invited Talk, Dept. of Industrial Machinery DX, KIMM, Daejeon
    \hfill (Title: \textit{SLAM, Spatial AI, and Human-Robot Interactive Navigation})

    \item 2025.10.30: Invited Talk, 2025 Fall Conference of The Korean Fiber Society, Busan
    \hfill (Title: \textit{Physical AI for Smart Factory})

    \item 2025.09.12: \textsf{학부생 커리어 설계 초청 강연}, KAIST Department of Civil and Environmental Engineering
    \hfill (Title: \textit{\textsf{건설도 하고 로봇도 하기 (Feat. 건설및환경공학과 학석박)}})

    \item 2025.08.21: \textsf{2025년 대구 디지털 혁신거점 조성지원 사업 -- 2025년 ABB분야 기술사업화 교육 운영 지원사업}
    \hfill (Title: \textit{\textsf{Visual Servoing 기반의 Peg-in-Hole 작업 수행을 위한 로봇공학 개론}})

    \item 2025.08.15: AI Robotics KR 2025: Physical Intelligence for the Real World
        \hfill (Title: \textit{Generative AI for Mobile Robot Navigation})

    \item 2025.07.21: DGIST Campus Tour Special Lecture (Hosan High School)

    \item 2025.07.18: \textsf{2025년 영상이해 및 영상처리연구회 합동 여름학교} (IEIE)
        \hfill (Title: \textit{Generative AI for Mobile Robot Navigation})

    \item 2025.06.19: 2025 1st DeepTech Open Network Forum, Daegu Innopolis
    \hfill (Title: \textit{Eyes and Brains of a Humanoid})

    \item 2025.06.13: Robotics Lab Seminar on SLAM \& Perception, Hyundai Motor Group
    \hfill (Title: \textit{From Research to Service: Industrial Insights from Technology Commercialization})

    \item 2025.06.05: \href{https://sonnet.ai}{Sonnet.AI Research Meetup}
    \hfill (Title: \textit{APRL Lab Research Introduction})

    \item 2025.05.28: Daegu-Gyeongbuk Chapter, Korea Women Venture Association
    \hfill (Title: \textit{Eyes and Brains of a Humanoid})

    \item 2025.05.28: Mid-to-Long-Term Research Strategy Seminar, Daegu-Gyeongbuk Division, ETRI
    \hfill (Title: \textit{Spatial AI, from the 2000s to 2025})

    \item 2025.05.27: DeepTech Scale-up Valley Innovation Council \& Industry-Academia Forum
    \hfill (Title: \textit{Eyes and Brains of a Humanoid})

    \item 2025.05.21/28: Special Lecture for Engineering Track, Posan High School Science Program
    \hfill (Topics: \textit{Introduction to 3D Vision and Digital Twin})

    \item 2025.04.26: Science Career Talk Concert, National Daegu Science Museum (Science Day)
    \hfill (Title: \textit{By 2035, Will Robots Outnumber Humans?})

    \item 2025.04.03: Technology Innovation Workshop, Technology Venture Leader Program (TVA), DGIST
    \hfill (Title: \textit{Toward the Era of General-Purpose Robots in Everyday Life})

    \item 2023.11.25: \href{https://drive.google.com/file/d/1h5sMgkyGGA8X2gxJUEzWCSwX9RlujNpe/view?usp=sharing}{SLAM KR 2023 Offline Event} (Why IMU Fusion for LiDAR SLAM?) \href{https://bit.ly/20231125_slamkr_giseopkim}{[Slide]}

    \item 2023.10.26: Autonomous IoT Research Center, \href{https://www.keti.re.kr/eng/main/main.php}{KETI} (Robotic Mapping and Localization for Autonomous Driving in AI era) \href{https://bit.ly/408J7XJ}{[Slide]}

    \item 2022.11.09: \href{https://ib.unist.ac.kr/robust-slam-simultaneous-localization-and-mapping-for-large-scale-urban-mapping-and-autonomous-driving/}{AIGS, UNIST} (Robotic Mapping and Localization for Autonomous Driving) \href{https://docs.google.com/presentation/d/1RLrrxGzzGWEgUQMvdWH0wNfsyn6ML2Hjw88PmgdrvlQ/edit?usp=sharing}{[Slide]}

    \item 2022.08.25: \href{https://rpm.snu.ac.kr/}{RPM Robotics Lab}, SNU (Optimization Tutorial with Hands-on Experiences using SymForce) \href{https://docs.google.com/presentation/d/1Z1FjnphgP60jTIa6da8vwhaAEzULefLrPQsJ4yBHAJA/edit?usp=sharing}{[Slide]}

    \item 2022.07.14: \href{https://sites.google.com/view/sparo/홈}{SPARO Lab}, Inha Univ. (LiDAR-based Lifelong Robotic Mapping in Changing Environments) \href{https://docs.google.com/presentation/d/1Muld60rT7KY_FaN4hyRaPHR2FsPkLV8z7fz7rYQzIv4/edit?usp=sharing}{[Slide]}

    \item 2021.05.31: \href{https://sites.google.com/view/radar-robotics/home}{ICRA 21 Radar Workshop} (MulRan Dataset for Urban Place Recognition) \href{https://www.youtube.com/watch?v=jFvKW9Kj8Ts}{[Video]}, \href{https://www.dropbox.com/s/dknylah6b7rizr8/20210531\%20icra\%20ws\%20mulran\%20v3.pptx?dl=0}{[Slide]}

    \item 2020.10.22: \href{http://soslab.co/}{SOS LAB} (Robust LiDAR SLAM in Complex Urban Sites) \href{https://www.dropbox.com/s/p30dpjqjbjhq69x/20201022\%20SOSLAB\%20talk\%20Giseop\%20Kim\%20share.pdf?dl=0}{[Slide]}

    \item 2020.01.30: \href{https://www.naverlabs.com/}{NAVER LABS} (Structural Place Recognition in Complex and Changing Urban Sites) \href{https://www.google.com/url?q=https\%3A\%2F\%2Fwww.dropbox.com\%2Fs\%2Fcoul2elzlulbj1j\%2FStructural\%2520Place\%2520Recognition\%2520in\%2520Complex\%2520and\%2520Changing\%2520Urban\%2520Sites.pptx\%3Fdl\%3D0&sa=D&sntz=1&usg=AFQjCNF6McgylrY6kU5KmqvCLC6_n-TzIw}{[Slide]}
\end{itemize}

%-------------------------
% research_collaborators
%-------------------------
\section{Research Collaborators}

\begin{itemize}[label=$\cdot$]
    \item Prof. \href{}{Myung-Hwan Jeon}, KIT, Korea
    \item Prof. \href{}{Daeun Song}, Ewha Womans University, Korea
    \item Prof. \href{}{Xuesu Xiao}, George Mason University, USA
    \item Prof. \href{}{Hyeonwoo Yu}, SKKU, Korea
    \item Dr. \href{}{Sunwook Choi}, NAVER LABS, Korea
    \item Prof. \href{}{Younggun Cho}, Inha University, Korea
    \item Prof. \href{https://ayoungk.github.io}{Ayoung Kim}, SNU, Korea
\end{itemize}

%-------------------------------------------
\bibliographystyle{plain}
\nobibliography{ref}

\noindent\rule{\textwidth}{0.4pt}
\vspace{1mm}
\hfill Revised \today

\end{document}