\section{Funded Projects}

\vspace{1mm}
\begin{pubSubsectionNum}{At DGIST (2024--)}
    \item 2025 (6 months, Jul to Dec). Title: N-HRHR (High-risk High-return project), DGIST. Funded by: DGIST. Role: PI.
    \vspace{-1mm}
    \item 2025--2029. Title: InnoCORE Research Program (DGIST Team topic: Physical AI for Bio-Embodied Systems). Funded by: Ministry of Science and ICT, South Korea. Role: Core Researcher, DGIST.
    \vspace{-1mm}
    \item 2025--2030. Title: AI Star Fellowship Program (Top-tier Young AI Researcher Support). Funded by: Ministry of Science and ICT, South Korea. Role: Core Researcher, DGIST.
    \vspace{-1mm}
    \item 2025--2028. Title: Start-up Fund. Funded by: DGIST. Role: PI.
    \vspace{-1mm}
\end{pubSubsectionNum}

\begin{pubSubsectionNum}{Before DGIST (--2021)}
    \item 2021. Title: Development of technology for analyzing and predicting disaster risks in urban spaces of urban regeneration areas. Funded by: KAIA, MOLIT of South Korea (in total 1,796,000,000 KRW). Role: Developing portable 3D mapping system and software. 
    \vspace{-1mm}
    \item 2020--2021. Title: Towards long-term autonomy through introduction of the temporal domain into spatial representations used in robotics. Funded by: Bilateral Research Exchange Support Program of NRF, South Korea (in total 40,000,000 KRW) and The Czech Science Foundation (GACR). Role: Joint research with Professor Tomas Krajnik of Czech Technical University in Prague.
    \vspace{-1mm}
    \item 2018--2020, Title: Localization techniques on 3D SLAM maps using LiDAR and Camera sensors (2018), Development of SLAM technology based on LiDAR and Camera sensors using deep learning (2019), Localization in changing city (2020). Funded by: NAVER LABS. Role: Lead researcher.
    \vspace{-1mm}
    \item 2018--2019. Title: Automated urban analysis techniques using 3D sensor data (creation of 100m scale perceptible regions and topological maps). Funded by: KAIA, MOLIT of South Korea (in total 370,000,000 KRW). Role: Lead researcher.
    \vspace{-1mm}
    \item 2018. Title: 3A Localization -- Anytime Anywhere Anyview Robot Localization at Complex Urban. Funded by Master's and Doctorate Adventure Research Project, KAIST (in total 4,500,000 KRW). Role: Lead researcher.
\end{pubSubsectionNum}